Supporting Information

### 2021-09-01 vertical-thermal-review.Rmd
a bit of cleanup

appendix_NEON_methods_title<- "Methods S1. Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods S2. Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods S3. Methods for literature review"

@@

#SI table captions
NEON_sites_legend = "Table S1. (Neon sites)"
Tealeaves_parameters_legend <- "Table S2. (Tealeaves parameters)"

>>>>

appendix_NEON_methods_title<- "Methods S1. Methods for analyzing vertical gradients in the biophysical environment"
appendix_tealeaves_methods_title <- "Methods S2. Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods S3. Methods for literature review"

@@

#SI table captions
NEON_sites_legend = "Table S1. National Ecological Observatory Network (NEON) sites included in the analysis of vertical gradients of key biophysical characteristics"
Tealeaves_parameters_legend <- "Table S2. (Tealeaves parameters)"

### 2021-09-01 vertical-thermal-review_SI.Rmd
a bit of cleanup

---
title: ''
output: word_document
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

METHODS ON NEON ANALYSIS GO HERE.

>>>>

---
title: 'Supporting Information'
output: word_document
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

METHODS ON NEON ANALYSIS GO HERE. Google doc: https://docs.google.com/document/d/1HdPa7X5AMrEwfLjazGMU92uTYMc6pObh/edit#heading=h.gjdgxs
